Pillar 1 - Sequential Pattern Mining

### 2019-02-11 Pillar 1 - Sequential Pattern Mining.Rmd
computes SR_TPF manually

>>>>

SR_TPF are manually computed
```{r}
# current, past, not_yet
SR_TPF <- d_cumulative_transcript                  %>%
  select(sequenceID, eventID, item, course_not)    %>%
  unnest(item, .drop = F)                          %>%
  unnest(course_not)                               %>%
  left_join(
    select(d_transactions, 
           sequenceID, eventID, item, PF), 
    by= c("sequenceID", "eventID", "item")
    )                                              %>%
  select(sequenceID,eventID, course_not, item, PF) %>%
  rename(
    lhs="course_not", 
    rhs.x = "item", 
    rhs.PF = "PF")                                 %>%
  mutate(num_transactions = n())                   %>%
  group_by(lhs)                                    %>%
  mutate(
    num_lhs = n(),
    support_lhs         = num_lhs / num_transactions
    )                                              %>%
  group_by(rhs.x)                                  %>%
  mutate(
    num_rhs.x           = n(),
    support_rhs.x       = num_rhs.x / num_transactions
         )                                         %>%
  group_by(rhs.x,rhs.PF)                           %>%
  mutate(
    num_rhs.PF          = n(),
    support_rhs.PF      = num_rhs.PF / num_transactions
  )                                                %>%
  group_by(lhs, rhs.x)                             %>%
  mutate(
    num_rule_x          = n(),
    support_rule_rhs.x  = num_rule_x / num_transactions
  )                                                %>%
  group_by(lhs, rhs.x, rhs.PF)                     %>%
  mutate(
    num_rule_PF          = n(),
    support_rule_rhs.PF  = num_rule_PF / num_transactions,
    support_rhs_bounded  = num_rule_PF / num_rule_x
         )                                         %>%
  ungroup()                                        %>%
  mutate(
    confidence                   = support_rule_rhs.PF / support_lhs,
    confidence_bounded           = support_rhs_bounded / support_lhs, #not sure about this 
    lift                         = confidence / support_rhs.PF,
    lift_bounded                 = confidence_bounded /support_rhs_bounded #not sure about this
  )
```
